---
title: "News Magazines"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readxl)
library(lubridate)
library(urca)
library(tseries)
library(seasonal)
library(lmtest)
library(vars)
library(forecast)
library(graphics)
library(Hmisc)
library(xtable)
library(stargazer)

# Theming
quartzFonts(
  Roboto =
    c("Roboto-Light",
      "Roboto-Bold",
      "Roboto-Regular",
      "Roboto-Thin")
)

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      panel.border = element_blank()
    )
)

rm(list=ls())

col <- rcartocolor::carto_pal(12, "Bold")
source("func/helper_functions.R")
```

```{r message=FALSE, warning=FALSE}
# Load Data
sales <- read_excel("../data/sales.xls")
ads <- read_excel("../data/ads.xls")
adprice <- read_excel("../data/adprice.xls")
```

# Prepare and explore data

... combine the dataframes

```{r message=FALSE, warning=FALSE}
df <- sales %>%
  dplyr::select(-Status) %>%
  left_join(., ads %>%
              dplyr::select(- Status), 
            by = c("Titel","Heft Nr.")) %>%
  left_join(., adprice %>%
              dplyr::select(-Status),
            by = c("Titel","Heft Nr.")) %>%
  mutate(year = as.numeric(substrRight(`Heft Nr.`, 4)),
         issue = as.numeric(substr(`Heft Nr.`,1,2)))
```

```{r}
ggplot(df, aes(Gattung)) +
  geom_bar(fill = col[2], alpha = 0.8) +
  coord_flip()
```

```{r}
df %>%
  filter(Gattung == "Aktuelle Zeitschriften und Magazine") %>%
  ggplot(aes(Titel)) +
  geom_bar(fill = col[3], alpha = 0.8) +
  coord_flip()
```

## FOCUS, Der Spiegel, Stern

... keep only FOCUS, Der Spiegel, Stern

```{r}
keep <- c("FOCUS","Der Spiegel","Stern")

fss <- df %>%
  filter(Titel %in% keep) %>%
  mutate(date = calculate_week(issue, year))
```

```{r}
ggplot(fss, aes(date, `Verkauf Gesamt`,
                color=Titel)) +
  geom_line() +
  labs(x="", color="", title = "Verkauf Gesamt")
```

```{r}
ggplot(fss, aes(date, `Anzeigen Gesamt`,
                color=Titel)) +
  geom_line() +
  labs(x="", color="", title = "Anzeigen Gesamt")
```

```{r fig.height=4, fig.width=8}
ggplot(fss, aes(date, `Umsatz Brutto TEUR`,
                group=Titel, color = Titel)) +
  geom_line() +
  #facet_wrap(~Titel, nrow=1) +
  labs(x="", color="", title = "Umsatz Brutto TEUR")
```

```{r fig.height=4, fig.width=8}
ggplot(fss, aes(date, `Preis 4C 1/1`,
                group=Titel, color = Titel)) +
  geom_line() +
  #facet_wrap(~Titel, nrow=1) +
  labs(x="", color="", title = "Preis 4C 1/1")
```

```{r fig.height=4, fig.width=8}
ggplot(fss, aes(date, Heftumfang,
                group=Titel, color = Titel)) +
  geom_line() +
  #facet_wrap(~Titel, nrow=1) +
  labs(x="", color="", title = "Heftumfang")
```

# CCF

We use the cross correlation function (CCF) to estimate the relationship between two time series ($y_t$ and $x_t$). However, one difficulty is that the CCF is affected by the time series structure of the x-variable and any “in common” trends the $x$ and $y$ series may have over time.

One strategy for dealing with this difficulty is called “pre-whitening.”  The steps are:

  1) Determine a time series model for the x-variable and store the residuals from this model.

  2) Filter the y-variable series using the x-variable model (using the estimated coefficients from step 1). In this step we find differences between observed y-values and “estimated” y-values based on the x-variable model.

  3) Examine the CCF between the residuals from Step 1 and the filtered y-values from Step 2.  This CCF can be used to identify the possible terms for a lagged regression.
  
This strategy stems from the fact that when the input series (say, wt) is “white noise” the patterns of the CCF between wt and zt, a linear combination of lags of the wt, are easily identifiable (and easily derived).  Step 1 above creates a “white noise” series as the input.  Conceptually, Step 2 above arises from a starting point that y-series = linear combination of x-series.  If we “transform” the x-series to white noise (residuals from its ARIMA model) then we should apply the transformation to both sides of the equation to preserve an equality of sorts.


## Prewhitening / ARIMA

```{r}
# min <- calculate_week(33, 2013)
# max <- calculate_week(33, 2015)

min <- min(fss$date)
max <- max(fss$date)

fss %>%
  dplyr::select(`Verkauf Gesamt`, date, Titel) %>%
  spread(Titel, `Verkauf Gesamt`) %>%
  filter(date >= as.Date(min)) %>%
  filter(date <= as.Date(max)) %>%
  dplyr::select(-date) -> tempdf
```
  
```{r}
results <- list()
mag <- names(tempdf)
x <- 1

for (i in mag) {
    selected <- tempdf[, -which(names(tempdf) == i)]
    temp <- auto.arima(tempdf[,i], xreg = cbind(selected[,1],
                                             selected[,2]))
    results[[x]] <- temp
    x <- x+1
  }


resid <- cbind(results[[1]]$residuals, results[[2]]$residuals, results[[3]]$residuals)
```

```{r}
autoplot(resid) +
  scale_color_manual(labels = mag, values = col[1:3]) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(y="residuals", x="", color = "",
       title = paste("Timespan:", min,"to", max)) 
```

### Calculate CCF

```{r}
corr_temp <- resid %>% as.data.frame()
names(corr_temp) <- mag

# Create empty matrix
corr <- expand.grid(names(corr_temp), names(corr_temp))

corr$`-3` <- NA
corr$`-2` <- NA
corr$`-1` <- NA
corr$`0` <- NA
corr$`1` <- NA
corr$`2` <- NA
corr$`3` <- NA
  
x <- 1
  
for (corr1Id in 1:ncol(corr_temp)) {
    c1 = corr_temp[,corr1Id]

    for(corr2Id in 1:ncol(corr_temp)) {
      c2 = corr_temp[,corr2Id]
      correlation = ccf(c1, c2, lag.max = 3, 
                        na.action = na.contiguous,
                        plot=F)
      
      corr[x,3:9] <- correlation$acf %>% 
        as.data.frame() %>% t()
    
      x<- x+1
    }
}
```

#### Plot CCF

In R, the sample CCF is defined as the set of sample correlations between $x_{t+h}$ and $y_t$ for $h = 0, ±1, ±2, ±3$, and so on. A negative value for $h$ is a correlation between the x-variable at a time before $t$ and the y-variable at time $t$. For instance, consider $h = −2$.  The CCF value would give the correlation between $x_{t-2}$ and $y_t$.

In the following figure, each $x$-time series is plotted in its own plot. The color indicates the $y$-series. 

```{r}
# Calculate confidence intervals
ci_upper <- 2/sqrt(length(resid[,1]))
ci_lower <- -2/sqrt(length(resid[,1]))

# convert dataframe to long format
corrLong <- corr %>%
    gather(lag, ccf, `-3`:`3`) %>%
  mutate(lag = as.numeric(lag))
```

```{r}
corrLong %>%
  filter(Var1!=Var2) %>%
  ggplot(aes(lag,ccf,
             fill=Var1)) +
  geom_col(position = "dodge",
           #show.legend = F,
           alpha=0.8) +
  scale_fill_manual(values=col) +
  facet_wrap(~Var2, ncol=3)+
  scale_x_continuous(breaks = c(-3:3)) +
  geom_hline(yintercept = ci_upper, 
             color = "black",
             size = 0.3,
             linetype = 2)+
  geom_hline(yintercept = ci_lower, 
             color = "black",
             size=0.3,
             linetype = 2)+
  labs(x="", fill="", title = paste("Timespan:", min,"to", max))
```

